A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-03-19 paper/submission/prab.tex
edits to new bib entries

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research and practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Despite the success of on-line models in some facilities~\cite{xiaobiao}, 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators is a common method used at many research facilities.
When the beam dynamics is nonlinear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
This further complicates any mult-objective optimization by complicating the model. 
In order to be able to reliably identify optimal configurations of
  accelerators, we solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning parameters.
  This approach has been used in the past with much 
  success~\cite{bazarov05,yrss:09,chao09, hofler13,jefferson,gong15, gongthesis15,gull1,gull2,marija}.
The difference here being the implementation and application to a 
problem at the Argonne Wakefield Accelerator Facility (AWA).

>>>>

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research and practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Despite the success of on-line models in some facilities~\cite{xiaobiao}, 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators is a common method used at many research facilities.
When the beam dynamics is nonlinear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
This further complicates any mult-objective optimization by complicating the model. 
In order to be able to reliably identify optimal configurations of
  accelerators, we solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning parameters.
  This approach has been used in the past with much 
  success~\cite{bazarov05,yrss:09,chao09,gong12,hofler13,jefferson,gong15,gongthesis15,gull1,gull2,marija}.
The difference here being the implementation and application to a 
problem at the Argonne Wakefield Accelerator Facility (AWA).
